\thesistitle

### 2019-08-25 sections/introduction.tex
Introduction

Duplication in source code, also known as ``code clones'', is often seen as one of the most harmful types of technical debt. If the clone is altered at one location to correct an erroneous behavior, you cannot be sure that this correction is applied to all the cloned code as well \cite{ostberg2014automatically}. Additionally, the codebase size increases unnecessarily and so increases the amount of code to be handled when conducting maintenance work, as code clones can contribute up to 25\% of the code size \cite{bruntink2005use}.

Automating the refactoring process of code clones can help to deal with duplication problems. It can also assist in the evaluating whether refactoring a specific clone would improve the codebase, by using established metrics \cite{heitlager2007practical} to determine whether the code after applying the refactoring has improved. Howeverm clones detected on basis of established clone definitions \cite{roy2007survey} may not always be suitable for automated refactoring.

In this study, we define clones such that they can be automatically refactored and build a tool to automatically refactor such clones. This allows us to obtain before- and after-refactoring snapshots of software systems. We use software maintainability metrics to measure the impact of these refactorings. We also look into what variability we can allow between code fragments to still consider them clones, while still improving maintainability when refactoring these clones. Furthermore, we look into the thresholds that should be used while detecting clones to find clones that should be refactored.

We perform several quantitative experiments on a large corpus of open-source software to collect statistical data. With these experiments, we map the context of clones: where they reside in the codebase and what the relation is between duplicate fragments. We use the results to find appropriate refactoring opportunities for specific clones. We then automate the process of applying such refactorings, to be able to measure the impact on maintainability when refactoring clones found by certain definitions and thresholds.

@@

A study by Batova et al. \cite{bavota2012does} shows that the process of refactoring often leaves side effects in the code. This study reports that refactorings moving components in the inheritance hierarchy of object-oriented software tend to induce faults very frequently. This suggests that more accurate code inspection or testing activities are needed when such refactoring techniques are performed. Those refactoring techniques often have to be used when dealing with duplication in software \cite{fowler2018refactoring, fontana2015duplicated}. Because of that, refactoring code clones has been empirically shown to cause bugs or other side effects in code.

@@

Not in all cases will refactoring duplicated code result in a more maintainable codebase. Because of that, we compare the refactored code to the original code and measure the difference in maintainability. To do this, we use a practical model consisting of metrics to measure maintainability \cite{heitlager2007practical}. Based on this, we look into what \textit{thresholds} result in better maintainable code when refactored. This results in our final research question:
\begin{displayquote}
\textbf{Research Question 3:}\\What are the discriminating factors to decide when a clone \textbf{should} be refactored?
\end{displayquote}

@@

\subsection{Identification}
There are many tools to detect clones. The goal of most of these tools is to assist developers in reducing duplication in their code, i.e. assisting in the refactoring process. The problem is that these tools have no insight in the impact of refactoring such clones on the maintainability of the software. In this study, we can analyze a before- and after-refactoring snapshot of the code to determine the impact. If the maintainability increases after refactoring, this gives a strong indication that the clone should be refactored. This way the results of our study can support the clone identification process.

@@

\subsection{Naming Declarations}
Our automated refactoring model can create new methods, classes and interfaces when refactoring clones. Each of these declarations needs to have a name. Because the quality of the name will not have an impact on the maintainability metrics we use, finding appropriate names for automatically refactored code fragments is out of the scope for this study. For our automated refactoring efforts, we will use generated names for these declarations. %This may decrease the usefulness of the results of this research for refactoring-assistance.

>>>>

Duplication in source code, also known as ``code clones'', is often seen as one of the most harmful types of technical debt \cite{fowler1999refactoring}. If the clone is altered at one location to correct an erroneous behavior, you cannot be sure that this correction is applied to all the cloned code as well \cite{ostberg2014automatically}. Additionally, the size of the codebase increases unnecessarily and so increases the amount of code to be handled when conducting maintenance work, as code clones can contribute up to 25\% of the code size \cite{bruntink2005use}.

Automating the refactoring process of code clones can help to deal with duplication problems. It can also assist in the evaluation whether refactoring a specific clone would improve the codebase, by using established metrics \cite{heitlager2007practical} to determine whether the code after applying the refactoring has improved. However, clones detected on the basis of established clone definitions \cite{roy2007survey} may not always be suitable for automated refactoring.

In this study, we define clones such that they can be automatically refactored and build a tool to automatically refactor such clones. This allows us to obtain before- and after-refactoring snapshots of software systems. We use software maintainability metrics to measure the impact of these refactorings. We also look into what variability we can allow between code fragments while still improving maintainability when refactoring these clones. Furthermore, we look into the thresholds that should be used while detecting clones to find clones that should be refactored.

We perform several quantitative experiments on a large corpus of open-source software to collect statistical data. With these experiments, we map the context of clones: where they reside in the codebase and what the relation is between duplicate fragments. We use the results to find appropriate refactoring opportunities for clones in a specific context. We then automate the process of applying such refactorings, to measure the impact on maintainability when refactoring clones found by certain definitions and thresholds.

@@

A study by Batova et al. \cite{bavota2012does} shows that the process of refactoring often leaves side effects in the code. This study reports that refactoring techniques to remove duplicate code tend to cause faults very frequently. This suggests that more accurate code inspection or testing activities are needed when such refactoring techniques are performed. Because of that, refactoring code clones has been empirically shown to cause bugs or other side effects in code.

@@

Not in all cases will refactoring duplicated code result in a more maintainable codebase. Because of that, we compare the refactored code to the original code and measure the difference in maintainability. To do this, we use a practical model consisting of metrics to measure maintainability \cite{heitlager2007practical}. Based on this, we look into what \textit{thresholds} to use to find clones that result in better maintainable code when refactored. This results in our final research question:
\begin{displayquote}
\textbf{Research Question 3:}\\What are the discriminating factors to decide when a clone \textbf{should} be refactored?
\end{displayquote}

@@

\subsection{Identification}
There are many tools to detect clones. The goal of most of these tools is to assist developers in reducing duplication in their code, i.e. assisting in the refactoring process. The problem is that these tools have no insight into the impact of refactoring such clones on the maintainability of the software. In this study, we can analyze a before- and after-refactoring snapshot of the code to determine the impact. If the maintainability increases after refactoring, this gives a strong indication that the clone should be refactored. This way the results of our study can support the clone identification process.

@@

\subsection{Naming Declarations}
Our automated refactoring tool can create new methods, classes, and interfaces when refactoring clones. Each of these declarations needs to have a name. Because the quality of the name will not have an impact on the maintainability metrics we use, finding appropriate names for automatically refactored code fragments is out of the scope for this study. For our automated refactoring efforts, we will use generated names for these declarations. %This may decrease the usefulness of the results of this research for refactoring-assistance.
